\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\pagestyle{empty}
\linespread{1.05}
\begin{document}
\section*{Summary}


\subsection*{Overview}
\vspace{-0.1in}
This proposal aims to advance mathematical modeling, analysis, and
numerical simulations of collective dynamics and self-assembly arising
from attractive interactions between dipolar/nematic particles in a
suspension. Physicists model such a self-assembly using particles
possessing a biphasic material label on either half, with one more
hydrophobic than the other. Hydrophobic surfaces experience a
non-additive long-range attraction called the hydrophobic force. This
force is a major source of nonspecific interactions in biology and soft
matter. Despite its ubiquity, theoretical developments explaining its
basic underlying principles have come relatively late. Motivated by its
broad applicability, the PIs recently developed a novel and intuitive
mathematical model, called the hydrophobic attraction potential model,
based on the linear response of water to surface perturbations. This
model was used to show, for the first time, self-assembly of such
bipolar particles into vesicle-like structures using moving domain
elliptic partial differential equations (PDEs).

%This proposal aims to advance mathematical modeling and analysis of
%collective dynamics of amphiphilic self-assembly. Amphiphilic particles
%such as lipid molecules possess both hydrophobic and hydrophilic
%surfaces and self-assemble into meso/macroscopic structures such as
%micelles and bilayers of lipids. Experimentalists model self-assembly
%using Janus particles—spherical particles possessing a biphasic material
%label on either hemisphere. Janus particles have been widely used in
%soft matter physics as a model amphiphilic colloid and can be designed
%for catalytic activity or stimuli-responsive smart materials.

%Hydrophobic surfaces experience a nonadditive long-range attraction
%called the hydrophobic force. This force is a major source of
%nonspecific interactions in biology and soft matter. Despite its
%ubiquity, theoretical developments explaining its basic underlying
%principles have come relatively late. Motivated by its broad
%applicability, the PIs recently developed a novel and intuitive
%mathematical model, called the hydrophobic attraction potential model,
%based on the linear response of water to surface perturbations. This
%model was used to show, for the first time, self-assembly of Janus
%particles into vesicle-like structures using a partial differential
%equation-based particle interaction.

The PIs propose to analyze the elliptic PDEs, develop fast and accurate
numerical algorithms, and apply their hydrophobic attraction potential
model to more general self-organization dynamics. They aim to generalize
the linear-response model to a wider class of hydrophobic interactions,
and numerically implement these interactions using integral equation
formulations. Finally, they will develop a coarse-grained model based on
the kinetic theory to investigate the rheological properties of the
assembly of particles with tunable hydrophobicity. The unifying aspects
of the project will establish a platform for efficiently simulating
the collective dynamics of large numbers of particles, and focus on
rigorous, mathematical analysis of the underlying model equations in
complex geometries. The project supports undergraduate and graduate
student collaborators.

\subsection*{Intellectual Merit}
\vspace{-0.1in}
This collaborative project focuses on modeling, simulation, and analysis
of self-assembly and collective dynamics of granules. The main
ingredient is a nonlocal interaction through the solution of an moving
domain elliptic PDE that encompasses long-range amphiphilic and
short-range steric interactions. The PIs have validated this
coarse-grained model against well-known vesicle hydrodynamics. The
technical research tasks include quantifying collective properties of
amphiphilic ensembles, improving on mathematical models, efficient,
high-order numerical algorithms for large-scale two- and
three-dimensional simulations with confinement, and developing a kinetic
theory for the collective dynamics.

%The purpose of this research is to reach interesting physical phenomena
%with less computational cost than molecular dynamics, and account for
%more general features that continuum theory misses. The main ingredient
%is defining a nonlocal interaction through the solution of an elliptic
%boundary value problem that has the phenomenological characteristics of
%long-range hydrophobic attraction. This minimal model, while intuitive,
%is quite a general description of amphiphiles in solvent and gives rise
%to rich phenomena from Janus particle aggregates to correctly predicting
%elastic properties of bilayer. The technical research tasks include
%quantifying collective properties of amphiphilic ensembles, improving on
%mathematical models, efficient, high-order numerical algorithms for
%large-scale simulations, and incorporating external fields through
%electric charge.

\subsection*{Broader Impacts}
\vspace{-0.1in}
This project aims to advance the mathematical modeling of collective
dynamics of amphiphilic granules. The framework uses a new PDE-based
formulation that accounts for important and complex systems in soft
matter. These complex systems include optimal shape design in
metamaterials and fusion and fission of amphiphilic bilayer membranes.
The simulations will be performed with computational tools designed to
solve the governing PDEs both efficiently and with high-order accuracy.
The models describing granular systems could be transformative in
biomedicine and material science. The research draws from expertise in
scientific computing, physics of fluids, and mathematics. The
mathematical component incorporates leading variational techniques and
offers insight into fundamentals of self-organization and collective
dynamics. The project brings socially consequential research into the
classroom and offers undergraduates the opportunity to train alongside
faculty and graduate students. With its unique combination of
mathematical modeling, analysis, and scientific computing, the project
highlights the potential advancement of STEM from applied mathematics.


\end{document}

