\section{Relevant Results from Prior NSF Support}
\noindent {\bf Rolf Ryham}: no prior NSF support.

\noindent
{\bf Yuan-Nan Young}: {\em NSF-DMS-1222550, Mathematical and
experimental study of lipid bilayer shape and dynamics mediated by
surfactants and proteins}, \$212,603, 9/15/2012 - 08/31/2016 (with
no-cost extension), PI. {\em Intellectual merit:} The focus of this
grant is modeling the interaction between a pure lipid bilayer membrane
with surfactant, cholesterol, and protein.
%Hence, there is no overlap between these grants and the current proposal.

%YNY and collaborators have studied (1) asymmetry of lipid bilayer due to its interaction
%with proteins and surfactants, (2) the electrohydrodynamics of a LBM under an
%electric field, and (3) the coupling between LBM dynamics and a transmembrane protein,
%such as a mechanosensitive channel. 

\noindent
{\it Broader impacts:} 
One PhD student (Szu-Pei Fu) was funded to work with YNY, and work has
resulted in seven papers~\cite{Nganguia2013_PoF, Nganguia2013_PRE,
Young2014_JFM, Young2015_PoF, Nganguia2015_CiCP,
Pak2015_PNAS,fu2015pre}. YNY has been actively involved with promotion
of underrepresented students at NJIT. The other PhD student (Herve
Nganguia) is African. YNY has taught a broad spectrum of courses in
fluid mechanics and applied math modeling.

\noindent
{\bf Bryan Quaife}: {\em NSF DMS-2012560, Erosion, Transport, and
Dispersion in Granular and Porous Media}, \$249,636,
08/01/2020--07/31/2023, PI. {\em Intellectual Merit:} The goal of this
research is to develop high-order numerical methods to
simulate hydrological processes including erosion.

\noindent
{\it Broader impacts:} 
A third-year PhD student (Jake Cherry) has been assigned to this
project. One paper will be submitted before December
2021~\cite{lin-her-qua-che2021}.

\section{Project Management, Collaboration Plan, and Schedules of
Research Tasks}
\setlength{\parindent}{0pt}
% N.B. wrapfigure is not compatible with \noindent.

\begin{wrapfigure}[11]{r}{0.56\textwidth}
\vspace{-19pt}
%\definecolor{barblue}{RGB}{51,102,254}
%\renewcommand\sfdefault{phv}
%\renewcommand\mddefault{mc}
%\renewcommand\bfdefault{bc}
%\sffamily
\begin{ganttchart}[
    canvas/.append style={fill=none, draw=black!5, line width=.75pt},
        x unit =4.5mm,
        y unit chart =\baselineskip,
    hgrid style/.style={draw=black!5, line width=.75pt},
    vgrid={*1{draw=black!5, line width=.75pt}},
    title/.style={draw=none, fill=none},
    title label font=\bfseries\footnotesize, % numbers across the top
    title label node/.append style={below=3pt},
    include title in canvas=false,
    bar label font=\mdseries\footnotesize\color{black!70}, 
    % titles across the left
    %bar label node/.append style={left=2cm},
    bar/.append style={draw=none, fill=blue},
    bar incomplete/.append style={fill=blue},
    bar progress label font=\mdseries\footnotesize\color{black!70},
    milestone label font=\mdseries\small\color{black!70},
        milestone left shift =0.9,
        milestone right shift =0.1,
        % Don't draw group bars
        group height =0,
        group peaks height =0,
        group label font =\bfseries\small,
]{1}{12}
\gantttitle[
    title label node/.append style={below left=3pt and -6pt}
]{QUARTERS:\quad1}{1}
\gantttitlelist{2,...,12}{1} \\
%\ganttgroup{Tasks\hfill}{1}{12}\\
\ganttbar[bar/.append style={fill=red}]{Specific Aim 1}{1}{12} \\
\ganttbar[bar/.append style={fill=blue}]{Specific Aim 2}{1}{12}\\
\ganttbar[bar/.append style={fill=green}]{Specific Aim 3}{1}{12}\\
\ganttbar[bar/.append style={fill=black}]{Program Management}{1}{12}
\ganttbar[bar/.append style={fill=magenta}]{}{4}{4}
\ganttbar[bar/.append style={fill=magenta}]{}{8}{8}
\ganttbar[bar/.append style={fill=magenta}]{}{12}{12}
\end{ganttchart}
\vspace{-10pt}
\caption{Schedule for the proposed work, measured in quarters from the
  beginning of the project. The lead PI of each Specific Aim will be RR
  (red), BQ (blue), and YNY (green). Project management will be
  continuous (black), but we anticipate extra attention will be
  necessary to align objectives in quarters 4, 8, and 12 (magenta).}
\label{fig:schedule}
\end{wrapfigure}
\textbf{Project management}: 
%
The success of the proposed research requires complementary expertise
and collaborative efforts in physics, applied mathematics, algorithms,
and computing. PI RR has been working on mathematical modeling with a
strong analytical background. PI YNY has been working on many areas of
computational fluid dynamics and applications to math biology for many
years. PI BQ has been working on integral equation methods, fast
algorithms, and their applications to fluid dynamics for many years.
Their recent collaborative work on the HAP model in two
dimensions~\cite{FuQuRyYo20} has provided a solid foundation for the
proposed research.

\smallskip

\textbf{Collaboration plan}: 
%
The management responsibility of this collaborative research will reside
with the lead PI (RR) for this endeavor. The research work is structured
to meet the tasks discussed in \S\ref{sec:proposed-work}. The PIs,
postdocs, and students will meet frequently on Zoom and in person when
possible. During the pandemic, the three PIs will meet weekly on Zoom
for a research meeting. Once the pandemic is under control, PI RR and PI
YNY will conduct biweekly meetings in person, with PI BQ Zoom in from
Florida. The PIs will share software packages, paper sources, and
references on a common \textsf{Git} repository. The resulting software
packages will be posted on the \textsf{Github} software repository.

\smallskip

\textbf{Research Schedule:} The detailed schedule for the proposed work
is shown in Figure~\ref{fig:schedule}. Each PI will spearhead a
different Specific Aim, and program management will happen
throughout, with special coordination taken in quarters 4, 8, and
12.


