\subsection{Specific Aim 3: Dynamics of self-assembly by HAP under an external flow/field}
\label{subsec:specific_aim_3}

\subsubsection{Vesicles in background flows}
Numerically solving the Stokes and screened Laplace system~\eqref{SL}
and~\eqref{eq:stokes} is nontrivial, and we will develop efficient,
robust, high-order-in-time and -space algorithms suited to the problem.
There are a few challenges. {\bf (i)} The equations express a two-way
coupling since the flow changes the position of the suspended particles,
and in return, the geometry-dependent hydrophobic stresses impart a
force on the flow. {\bf (ii)} The inputs to the Stokes equations are
particle configurations, forces, and torques. The outputs are the rigid
body translation and angular velocities used to update the particle
positions (see Figure~\ref{fig:flow_map}). Although the underlying
equations are linear, the overall problem is highly nonlinear because
the domain is constantly changing. {\bf (iii)} Self-assembly causes the
particles to come into close contact. As a result, an exceptional
spatial accuracy is required to resolve the fields between adjacent
particles. Furthermore, physically relevant elastic properties of
bilayers become apparent at large length scales and for large
particle-numbers, which increases the computational complexity of our
simulations. 

We include a background flow by replacing the third equation in
\eqref{eq:stokes} with the condition $\mathbf{u}(\mathbf{x})
\to \mathbf{u}_{\infty}(\mathbf{x})$ as $|\mathbf{x}| \to
\infty$. To incorporate the far-field flow, we use the representation 
\begin{align}
\label{PowerMiranda}
  {\bf u} = {\bf u}_{\infty} + \mathcal{K}\boldsymbol{\eta} + 
    \sum_{i=1}^N \left(S(\cdot, {\bf a}_i) {\bf F}_i + 
                 R(\cdot, {\bf a}_i) {\bf G}_i\right),
\end{align}
where $S$ and $R$ are stokeslets and rotlets supported at the respective
particle centers~\cite{leal_2007} and $\mathcal{K}\boldsymbol{\eta}$ is a layer
potential for the unknown density function $\boldsymbol{\eta}$. With the
exception of the rigid body conditions, the
representation~\eqref{PowerMiranda} automatically satisfies all the
hydrodynamic equations including the far-field condition. The rigid
body conditions follow by requiring the viscous stresses to vanish across
the particle boundaries.
%
We will compare the behavior of our particle-based vesicles in Stokes
flow to well-established models that enforce area incompressibility and
volume conservation in vesicle membrane
dynamics~\cite{torres-sanchez_millan_arroyo_2019,mahapatra_saintillan_rangamani_2020, Steigmann99, C6SM02452A}.
\S \ref{sec:preliminary_work} contains our preliminary results.
%
%Our
%preliminary results show that the particle-based bilayers have the same
%large area modulus as real lipid bilayer membranes, so we expect
%realistic results from our flow simulations. Under moderate shear rates,
%the vesicle elongates and takes on the tank-treading elliptical shape.
%We can directly check for area compressibility and volume conservation
%properties from particle simulations by tracking the change in area
%density of the midplane as a function of shear flow rate, along with
%evaluating the tangential divergence of the velocity.
%
%Bilayer membranes have a small permeability to
%water~\cite{323e9a2f0c58487ea82518d7a1f96485}, and modelers often assume
%a vesicle membrane that conserves volume. In our particle-based
%approach, water motion across the bilayer is limited by the size of the
%gaps between the particles, which is an artifact of coarse-graining.
%Making these gaps smaller comes at the expense of numerical accuracy,
%and we will assess if there is a reasonable trade-off between
%approximate volume conservation and simulation complexity. 
%
%Finally, the particle-based vesicle bilayers have two distinct leaflets
%consisting of the particles in contact with the vesicle interior, and
%those in contact with the surrounding fluid. Since there is a nonzero
%separation between these layers, an important effect we observe is that
%the leaflets slide against one another under shear flow. This implies
%that part of the viscous dissipation in the aqueous phase is enhanced by
%intermonolayer friction~\cite{SHKULIPA2005823, ShkulipaThesis}.
%Intermonolayer slip enters zero-thickness membrane models as a velocity
%jump boundary condition and leads to multiple solution
%states~\cite{schwalbe_vlahovska_miksis_2010}. In the present proposal,
%intermonolayer slip is an artifact of monolayer independence and we can
%control for slip as a function of shear rate, vesicle diameter, and
%particle geometry.

\subsubsection{Electromechanical effects on the dynamic assembly of amphiphiles \label{subsubsec:em_effects}}
In recent experiments~\cite{FaizEtAl2019_SoftMatt}, membrane bending
rigidity was determined as a function of lipid composition from 0 to 100
mol $\%$ of charged lipids using flicker spectroscopy of the shape
fluctuations of a giant unilamellar vesicle (GUV).
%the bending rigidity is determined as a
%function of lipid composition from 0 to 100 mol $\%$ of charged lipids
%in recent experiments~\cite{FaizEtAl2019_SoftMatt}---
Membrane bending rigidity increases with increasing lipid surface
charge, but decreases with increasing salt concentration in the bulk
solution due to the screening of the lipid surface charge. This
result agrees
with several theoretical models~\cite{Kralchevsky1996_JCIS,
May1996_JChemPhys, LoubetEtAl2013_PRE} that also assume the quadratic
form of the elastic energy density in the presence of surface charge and
bulk charge~\cite{DuplantierGoldstein1990_PRL, Winterhalter1992_JPC}. As
the electrostatic interaction is non-local in nature, we expect that the
controversy of the HK elastic energy form (see
\S\ref{subsec:specific_aim_1}) would worsen in the presence of
electrostatic interactions and electrokinetics. The PIs will extend the
approaches in \S\ref{subsec:specific_aim_1} to charged lipids to
calculate the bending moduli and compare against the experimental
results in~\cite{FaizEtAl2019_SoftMatt}. We propose to incorporate an
explicit surface charge on each particle boundary $P_i$ and compute the
electrostatic potential as a functional of particle configuration.
Adding the electrostatic force to the hydrophobic attraction force
between particles, we will assess the dependence of elastic moduli on
electric charges using the methods described in
\S\ref{subsec:specific_aim_1}. Results from these proposed calculations
will provide further comparisons and validations of the HAP model
against the continuum mechanics.

Once the effects of lipid charges on the moduli are verified, the PIs
propose to examine how to use an external electric field to control the
amphiphilic self-assembly in solvent. PI YNY has a track record of
working on electrohydrodynamics of an elastic, inextensible membrane
using both asymptotic analysis~\cite{Nganguia2013_PRE, Young2014_JFM,
Young2015_PoF} and numerical simulations~\cite{Nganguia2015_CiCP} and
will work with both PIs RR and BQ to extend the HAP model to study the
electromechanical effects on the assembly of amphiphile. Results from
this research will yield a quantitative understanding of how to utilize
an electric field to achieve optimal control of assembly of amphiphiles
in solvent.




