\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\pagestyle{empty}

\begin{document}
\begin{center}
{\bf \Large Summary}\\ Collaborative Research
\begin{tabular}{ccc}\\ 
Fordham University & Florida State University& New Jersey Institute of Technology\\
Rolf Ryham &            Bryan Quaife &              Yuan-Nan Young
\end{tabular}

\end{center}

\subsection*{Overview}
This proposal aims to advance mathematical modeling and analysis of collective dynamics of amphiphilic self-assembly.  Amphiphilic particles such as lipid molecules possess both hydrophobic and hydrophilic surfaces
that self-assemble into meso/macroscopic structures such as micelles and bilayers of lipids.  Experimentalists model self-assembly
using Janus particles, which have been widely used in soft matter physics as a model amphiphilic colloids and can be designed for catalytic activity or stimuli-responsive smart materials.

Amphiphilic self-assembly comes about due to a long-range attraction called the hydrophobic force.  This force is a major source of nonspecific interactions in biology and soft matter. Despite its ubiquity, theoretical developments explaining the basic underlying principles of the hydrophobic effect have come relatively late. Motivated by its broad applicability, the PIs recently developed a novel and intuitive mathematical model, called the hydrophobic attraction potential model, based on the linear response of water to surface perturbations. This model was used to show, for the first time, self-assembly into vesicle-like structures using a partial differential equation-based particle interaction.

The PIs propose to apply their hydrophobic attraction potential model to the self-organization dynamics of Janus particles.  They aim to generalize the linear response model to more general hydrophobic interactions, which will be numerically implemented using integral equation formulations.  Finally, they will investigate and simulate the hydrophobic interaction in the presence of electric charge and ions. The unifying aspects of the project are establishing a platform for efficiently simulating the collective dynamics at large scales, and the focusing on rigorous, mathematical analysis of the underlying model equations and complicated geometries.  The project supports undergraduate and graduate student collaborators. 

\subsection*{Intellectual Merit}
The purpose of this research is to reach interesting physical phenomena with less computational cost than molecular dynamics, and account for more general features that continuum theory misses. The main ingredient is defining a nonlocal interaction through the solution of an elliptic boundary value problem that has the phenomenological characteristics of long-range hydrophobic attraction. This minimal model, while intuitive, is quite a general description of amphiphiles in solvent and gives rise to rich phenomena from Janus particle aggregates to correctly predicting elastic properties of bilayer. The technical research tasks include quantifying collective properties of amphiphilic ensembles, improving on mathematical models, efficient, high-order numerical algorithms for large-scale simulations, and incorporating external fields through electric charge.


\subsection*{Broader Impacts}
This project aims to advance the mathematical modeling of collective dynamics of amphiphilic particles. The simulations use a new, yet intuitive, approach that accounts for important and complex systems that are presently out of reach in computational material science. These complex systems include optimal shape design in metamaterials and fusion and fission of amphiphilic bilayer membranes. The models describing colloidal systems could be transformative in biomedicine and material science. The research draws from expertise in scientific computing, physics of fluids, and mathematics. The mathematical component incorporates leading variational techniques and offers insight into fundamentals of material science. The project brings socially consequential research into the classroom and offers 
undergraduates the opportunity to train alongside faculty and graduate students. With its combination of mathematical modeling, analysis, and scientific computing, the project highlights the importance of mathematics and computation to all areas of science and engineering.
\end{document}
